A comparison of model-based and design-based approaches for spatial data.

### 2021-06-07 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
added to outline from model comparison papers.

define sampling design, define parameters, define model-based, etc.

@@

@@

@@

<!-- \citep{Cressie2015statistics, Schabenberger2017statistical} -->

@@

>>>>

define sampling design, define parameters, define model-based, sample, population, super-population?, etc.

@@

give some examples of possible spatial data

@@

brus2020statistical: most similar to what this paper will be, directly comparing the two approaches. This has a lot of other potentially useful references to go back to. (published in 2021 so likely doesn't have many that have cited it yet).

de1990model: early comparison of design v model in spatial context

@@

Other model based stuff:
chan2020bayesian: Bayesian model-based approach.
Based on splines: 
Cicchitelli, G. and Montanari, G. E. (2012). “Model-Assisted Estimation of a Spatial Population
Mean.” International Statistical Review, 80(1): 111–126.
<!-- \citep{Cressie2015statistics, Schabenberger2017statistical} -->

@@

sterba2009alternative: psychological context comparison, has a lot of the older background (e.g. Fisher, Neyman, etc.)

Cooper2006sampling: ecological context, also has a nice very general background comparing two approaches, introduces a "model-assisted" variance estimator.
